Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
minor fixes

\vspace{1ex}\noindent\textbf{Issue \#16, Table~\ref{tab:cross-testing}.}
\Igor{
  Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
  Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
  que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
  de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
  that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
  B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
  function declaration. The fuzzer removes the function declaration and 
  injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
  the break statement should throw an early error (in this case a SyntaxError) 
  if the break statement is not nested in an iterational or a switch statement. All engines works
  as expected but \veight{} pass without failures.
}

@@

\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:test-transplantation-bugs}.}
\Igor{to appear...}

>>>>

\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.}
\Igor{
  Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
  Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
  que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
  de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
  that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
  B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
  function declaration. The fuzzer removes the function declaration and 
  injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
  the break statement should throw an early error (in this case a SyntaxError) 
  if the break statement is not nested in an iterational or a switch statement. All engines works
  as expected but \veight{} pass without failures.
}

@@

\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:test-transplantation-bugs}.}
Esse bug foi reportado no engenho do \chakra{} e foi manifestado atraves 
de uma mutacao provinda do \radamsa{}. O test case eh descrito in Figure~\ref{xxx},
the
